\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,latexsym,paralist}

\DeclareRobustCommand{\stirling}{\genfrac\{\}{0pt}{}}

\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newtheorem*{solution}{Solution}
\newtheorem*{resources}{Resources}

\newcommand{\name}[1]{\noindent\textbf{Name: #1}}
\newcommand{\honor}{\noindent On my honor, as an Aggie, I have neither
  given nor received any unauthorized aid on any portion of the
  academic work included in this assignment. Furthermore, I have
  disclosed all resources (people, books, web sites, etc.) that have
  been used to prepare this homework. \\[1ex]
 \textbf{Signature:} \underline{\hspace*{5cm}} }

 
\newcommand{\checklist}{\noindent\textbf{Checklist:}
\begin{compactitem}[$\Box$] 
\item Did you add your name? 
\item Did you disclose all resources that you have used? \\
(This includes all people, books, websites, etc. that you have consulted)
\item Did you sign that you followed the Aggie honor code? 
\item Did you solve all problems? 
\item Did you submit the pdf file (resulting from your latex file)
  of your homework?
\item Did you submit a hardcopy of the pdf file in class? 
\end{compactitem}
}

\newcommand{\problemset}[1]{\begin{center}\textbf{Problem Set #1}\end{center}}
\newcommand{\duedate}[2]{\begin{quote}\textbf{Due dates:} Electronic
    submission the .pdf file of this homework is due on \textbf{#1} on e-campus
    (as a turnitin assignment), a signed paper copy
    of the pdf file is due on \textbf{#2} at the beginning of
    class. \end{quote} }

\newcommand{\N}{\mathbf{N}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\Z}{\mathbf{Z}}

\begin{document}
\problemset{1}
\centerline{CSCE 629 (Dr. Klappenecker) }

\duedate{9/6/2017 before 2:50pm}{9/6/2017}
\name{ (put your name here)}
\begin{resources} (All people, books, articles, web pages, etc. that
  have been consulted when producing your answers to this homework)
\end{resources}
\honor

\newpage%
\noindent Get familiar with \LaTeX. All exercises are from the lecture notes
(not from our textbook). \medskip

\begin{problem}
Sign up for your section on perusall.com (watch for e-mail with sign
up instruction). Read Chapter 10 on perusall.com. Make at least 5
insightful comments (these are automatically graded. Spread them out
over the chapter and do not make them too short, the system penalizes
for that). Endorse other comments if they are helpful. 
\end{problem}

\begin{problem}
Exercise 10.1
\begin{solution}
\end{solution}
\end{problem}

\begin{problem}
Exercise 10.2
\begin{solution}
\end{solution}
\end{problem}

\begin{problem}
Exercise 10.3
\begin{solution}
\end{solution}
\end{problem}

\begin{problem}
Exercise 10.9
\begin{solution}
\end{solution}
\end{problem}

\begin{problem}
Exercise 10.10 
\begin{solution}
\end{solution}
\end{problem}

\begin{problem}
Exercise 10.12
\begin{solution}
\end{solution}
\end{problem}

\begin{problem}
Exercise 10.17
\begin{solution}
\end{solution}
\end{problem}

\begin{problem}
Exercise 10.27
\begin{solution}
\end{solution}
\end{problem}

\begin{problem}
Exercise 10.28
\begin{solution}
\end{solution}
\end{problem}





Homeworks must be typeset in \LaTeX{}. 









\goodbreak
\checklist
\end{document}
